---
title: "G2- Final_Presentation"
author: "Mason Richins, Nathan Karren, Stirling Ewing"
date: "12/4/2021"
output: word_document
---

```{r setup, comment=NA ,include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(stargazer)
library(car)
library(effects)
library(corrgram)
library(wooldridge)
library(lmtest)
```


Cleaning up the NA's found in hrwage and lhrwage
```{r, comment=NA}
df <- sleep75
df <- df[complete.cases(df),]
```

We need to remove variables that we feel ar not relevant to the story

This is the data set that we will use for the regression on slpnaps. We need to remove the other leisure variables because they contradicted with the dependent variable. 
```{r, comment=NA}
df1 <- select(df, -c(leis1,sleep,smsa,prot,south, inlf, case, leis2, leis3, exper))
```


This is for an even stricter set of variables that we will use when regressing on slpnaps
```{r, comment=NA}
df2 <- select(df, c(slpnaps, hrwage, age, agesq, black, educ, gdhlth, male))

corrgram(df2, order=TRUE, lower.panel=panel.shade,upper.panel=panel.pie, text.panel=panel.txt,main="Correlations between variables")
```

Here is the summary of all the variables to give us an idea of the different variables
```{r, comment=NA}
summary(df1)
```

To test and see what the structure of data set is
```{r, comment=NA}
str(df1)
```

 leis1 , sleep , smsa, prot, south, worknrm, worksnd, inlf, case, leis2, leis3, exper

We removed all of the leis variables because it contradicts the slpnaps dependent variable.

(We removed sleep because we feel it would be more beneficial to use slpnaps and they both would show multicollinearity)

We removed smsa, prot, and south because they do not apply to the story we want to tell

We removed inlf and case because they resulted in errors appear in our data. 

Testing the initial MRM to see if it works
```{r, comment=NA}
MRM_sleep <- lm(slpnaps~ . , df1)
stargazer(MRM_sleep, type = "text")

hist(resid(MRM_sleep))
```

We should narrow down our regressions to only a few variables so we can more easily record that. 
Possible regressions
  (maybe we should adjust to regressing on slpnaps because    logically hrwage won't be affected by slpnaps.) 
  slpnaps ~ age + black + educ + gdhlth + hrwage + male + u
  slpnaps ~ age + black + educ + gdhlth + hrwage + male +     earns74 + selfe + spwrk + spsepay + totwork + yngkid +      yrsmarr + u
  slpnaps ~ age + agesq + black + educ + gdhlth + hrwage +    male + u
  log(slpnaps) ~ age + black + educ + gdhlth + hrwage +       male)
  
```{r, comment=NA}
reg_base <- lm((slpnaps/60) ~ age + black + educ + gdhlth + hrwage + male, df1)

reg_extend <- lm((slpnaps/60) ~ age + black + educ + gdhlth + hrwage + male + earns74 + selfe + spwrk75 + spsepay + totwrk + yngkid + yrsmarr, df1)

reg_quad <- lm((slpnaps/60) ~ age + agesq + black + educ + gdhlth + hrwage + male, df1)

reg_log <- lm(log(slpnaps) ~ age + black + educ + gdhlth + hrwage + male + totwrk, df1)

reg_interaction <- reg_extend <- lm((slpnaps/60) ~ age + black + educ + gdhlth + hrwage + male + earns74 + selfe + spwrk75 + spsepay + totwrk + yngkid + yrsmarr + yngkid:male, df1)

stargazer(reg_base,reg_extend,reg_quad, reg_log,reg_interaction, type = "text")
```

Testing for multicollinearity
```{r, comment=NA}
vif(reg_extend)
```


Testing for Heteroskedasticty
```{r, comment=NA}
bptest(MRM_sleep)
```
We fail to reject homoskedasticity 

